Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2020-05-20 paper2_JNLS/paper.tex
NM

	\new{We remark that Eq.~\eqref{SkewPred} bears similarity to a formula derived by Onorato \& Suret \cite{onorato2016twenty}, in the context of {\em constant-depth} KdV, that relates variations in skewness to variations in spectral bandwidth. Indeed, since $\eta_t \approx c \eta_x$ to leading order, the term $\var(\eta_x)$ in Eq.~\eqref{SkewPred} could be interpreted as approximately the spectral bandwidth. We note that an analogous formula has been derived for the nonlinear Schr{\"o}dinger equation relating kurtosis to bandwidth variations \cite{onorato2016origin}. The present study differs in that it predicts a moment-bandwidth relation for waves propagating over {\em variable} depth, where it is the depth change that creates system disequilibrium. A small transition region connects two near-equilibrium systems, i.e. one far upstream and one far downstream. The link between these two equilibrium states is made mathematically precise by the statistical matching condition \eqref{statmatch}, which is the key ingredient needed to derive Eq.~\eqref{SkewPred}. This is in contrast to the simpler situation of waves propagating over constant depth, where spectral variations and the associated moment variations arise from out-of-equilibrium initial conditions \cite{onorato2016twenty, onorato2016origin}.}

@@

\section*{Acknowledgements}
CTB acknowledges support from the IDEA grant at Florida State University, as well as from the Geophysical Fluid Dynamics Institute. 
MNJM acknowledges support from the Simons Foundation, award 524259. 
This research of A.J.M. is partially supported by the Office of Naval Research N00014-19-S-B001. 
D.Q. is supported as a postdoctoral fellow on the grant.

>>>>

	\new{We remark that Eq.~\eqref{SkewPred} bears similarity to a formula derived by Onorato \& Suret \cite{onorato2016twenty}, in the context of {\em constant-depth} KdV, that relates variations in skewness to variations in spectral bandwidth. Indeed, since $\eta_t \approx c \eta_x$ to leading order, the term $\var(\eta_x)$ in Eq.~\eqref{SkewPred} could be interpreted as approximately the spectral bandwidth. We note that an analogous formula has been derived for the nonlinear Schr{\"o}dinger equation relating kurtosis to bandwidth variations \cite{onorato2016origin}. The present study differs in that it predicts a moment-bandwidth relation for waves propagating over {\em variable} depth, where it is the depth change that creates system disequilibrium. A small transition region connects two near-equilibrium systems, i.e.~one far upstream and one far downstream. The link between these two equilibrium states is made mathematically precise by the statistical matching condition \eqref{statmatch}, which is the key ingredient needed to derive Eq.~\eqref{SkewPred}. This is in contrast to the simpler situation of waves propagating over constant depth, where spectral variations and the associated moment variations arise from out-of-equilibrium initial conditions \cite{onorato2016twenty, onorato2016origin}.}

@@

\section*{Acknowledgements}
CTB acknowledges support from the IDEA grant at Florida State University, as well as from the Geophysical Fluid Dynamics Institute. 
MNJM acknowledges support from the Simons Foundation, award 524259. 
This research of A.J.M. is partially supported by the Office of Naval Research ONR N00014-19-1-2286.
D.Q. is supported as a postdoctoral fellow on the grant.
